Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-06 paper.tex
Estimators

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes\footnote{Python does not actually
distinguish between public and private  attributes or methods. By convention
however, any identifier prefixed with an underscore is considered a non-public
part of the API~\citep{pythontut}.} and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, appropriate default hyper-parameter values are provided for all
built-in estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible out-of-box for
non-experts. Finally, the constructor of an estimator never performs any actual
learning, nor does it even see any training dataset. Its only goal
is to set the parameter values and freeze the behavior of the estimator.

@@

The algorithmic workhorse of most estimators, and one of the few methods
that all estimators have in common, is called \texttt{fit}.
Invoking this method causes the estimator to learn from a training set,
supplied as one or more arguments.
Its task, from an API point of view,
is to determine (via a learning algorithm) model-specific parameters
from a training set and set these as attributes on the estimator object,
which can then be used to transform data or make predictions.
As in other object-oriented machine learning libraries
(e.g.\ Weka's Java API)
no distinction is made in the type hierarchy
between what is variously called an estimator or a \textit{learner}
in the machine learning literature,
and the \textit{model} that results from applying an estimator to data.
When the \texttt{fit} method has been called,
an estimator object serves dual purpose as a model
(and is referred to as such in the documentation).

An example to clarify the partial application style
is the following code snippet.
If $X$ is a dataset in the format described below and $k$ is some integer,
then the Python code to train a $k$-means clustering model on it
can be written as
% XXX we could use Pygments for syntax highlighting
\begin{verbatim}
km = KMeans(n_clusters=k).fit(X)
\end{verbatim}
This snippet relies on the fact that the \texttt{fit} method
always returns the object it was called on (its ``\texttt{self}''),
making a method chaining style possible.

@@

A \texttt{fit} method is present even on objects
that perform seemingly mundane tasks such as vectorizing text documents
for subsequent learning.
Such classes, however, can be said to learn their vocabulary
from the training corpus,
and follow the conventions set out above.
Even those estimators that are entirely stateless and therefore
do not require a \texttt{fit} method to perform useful work,
nevertheless have such a method for consistency and composibility,
and to perform parameter validation.
Examples of this latter kind of objects are the normalizing transformer,
kernel approximation transformers
\citep{rahimi2007random, li2010random, vedaldi2010efficient},
% XXX is it relevant that they are exactly two? Propose s/two/the
and two feature extraction classes that implement the ``hashing trick''
\citep{weinberger2009}.

>>>>

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes\footnote{Python does not actually
distinguish between public and private  attributes or methods. By convention
however, any identifier prefixed with an underscore is considered a non-public
part of the API~\citep{pythontut}.} and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, appropriate default hyper-parameter values are provided for all
built-in estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible \textit{out-of-box}
for non-experts. Finally, the constructor of an estimator never performs
any actual learning, nor does it even see any training dataset. Its only goal is
to set the parameter values and freeze the behavior of the estimator.

The estimator interface also defines a \texttt{fit} method. Invoking this method
causes the estimator to learn from a training set (e.g., supplied as two arrays
\texttt{X} and \texttt{y} in supervised learning estimators). Its task, from an
API point of view, is to run a learning algorithm and to determine model-
specific parameters from the training data and set these as attributes on the
estimator object.

As an example, let us consider a supervised learning task using linear regression.
Given the API defined above, solving this problem is as simple as:
\begin{center}
\texttt{clf = LinearRegression(penalty="l1").fit(X, y)}
\end{center}
In this snippet, a \texttt{LinearRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence enabling $L1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the arrays \texttt{X} and
\texttt{y}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LinearRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}. Let us also note the snippet relies on the
fact that the \texttt{fit} method always returns the object it was called
on\footnote{I.e., the \texttt{self} argument it was called on.}, hence making
method chaining  possible.

In \textit{scikit-learn}, classical learning algorithms are not the only objects
to be implemented as estimators. For example, preprocessing routines (e.g.,
vectorization of text documents, scaling of attributes, etc) or feature
extraction techniques also implement the same interface. Even those estimators
that are entirely stateless and therefore do not require the \texttt{fit} method
to perform any useful work implement the estimator interface. As we will
illustrate in the next section, this design pattern is indeed of prime
importance for consistency, composition and parameter validation reasons.

\textbf{Predictors.}

\textbf{Transformers.}

@@

% The algorithmic workhorse of most estimators, and one of the few methods
% that all estimators have in common, is called \texttt{fit}.
% Invoking this method causes the estimator to learn from a training set,
% supplied as one or more arguments.
% Its task, from an API point of view,
% is to determine (via a learning algorithm) model-specific parameters
% from a training set and set these as attributes on the estimator object,
% which can then be used to transform data or make predictions.
% As in other object-oriented machine learning libraries
% (e.g.\ Weka's Java API)
% no distinction is made in the type hierarchy
% between what is variously called an estimator or a \textit{learner}
% in the machine learning literature,
% and the \textit{model} that results from applying an estimator to data.
% When the \texttt{fit} method has been called,
% an estimator object serves dual purpose as a model
% (and is referred to as such in the documentation).

% An example to clarify the partial application style
% is the following code snippet.
% If $X$ is a dataset in the format described below and $k$ is some integer,
% then the Python code to train a $k$-means clustering model on it
% can be written as
% % XXX we could use Pygments for syntax highlighting
% \begin{verbatim}
% km = KMeans(n_clusters=k).fit(X)
% \end{verbatim}
% This snippet relies on the fact that the \texttt{fit} method
% always returns the object it was called on (its ``\texttt{self}''),
% making a method chaining style possible.

% A \texttt{fit} method is present even on objects
% that perform seemingly mundane tasks such as vectorizing text documents
% for subsequent learning.
% Such classes, however, can be said to learn their vocabulary
% from the training corpus,
% and follow the conventions set out above.
% Even those estimators that are entirely stateless and therefore
% do not require a \texttt{fit} method to perform useful work,
% nevertheless have such a method for consistency and composibility,
% and to perform parameter validation.
% Examples of this latter kind of objects are the normalizing transformer,
% kernel approximation transformers
% \citep{rahimi2007random, li2010random, vedaldi2010efficient},
% % XXX is it relevant that they are exactly two? Propose s/two/the
% and two feature extraction classes that implement the ``hashing trick''
% \citep{weinberger2009}.

@@
